\documentclass[11pt]{article}
%\usepackage[usenames,dvipsnames]{xcolor}
%\usepackage{soul}
%\usepackage{graphicx}
%\usepackage{lineno}
%\linenumbers

%\usepackage{hyperref}
%\usepackage{booktabs}

%\usepackage{amssymb}
\usepackage{xspace}
%\usepackage{graphicx}
%\usepackage{todonotes}

%\usepackage{geometry}

\topmargin 0.0cm
\oddsidemargin 0.2cm
\textwidth 16cm 
\textheight 21cm
\footskip 1.0cm

%\definechangesauthor[name=1, color=blue]{r1}
%\definechangesauthor[name=2, color=teal]{r2}
%\definechangesauthor[name=3, color=orange]{r3}
%\definechangesauthor[name=4, color=violet]{ed}

\begin{document}

\noindent \today\\[2em]
Marios Karouzos, Senior Editor\\
Nature Astronomy\\

\bigskip

\noindent Dear Dr. Karouzos, \\

Please accept our heartfelt thanks for allowing us to resubmit this manuscript after such a long delay.  This past year has been challenging in many ways, and we are deeply appreciative that you have held the door open for us this long.  We are all still very excited by the discovery presented here, and feel it will be well received in the community.  

We provide two updated versions of the manuscript.  The ``changetext'' version includes line numbers and colored text, showing changes since the original submission.  The ``revised'' version is just the current manuscript text, without showing changes.  Our estimate of the relevant sizes in the revised document are:

\begin{itemize}
    \item Main Text : 2009 words.
    \item First Paragraph : 204 words.
    \item Main text contains 3 figures and 1 table.
    \item Figure 1 legend : 195 words
    \item Figure 2 legend : 283 words
    \item Figure 3 legend : 122 words
    \item Table 1 legend : 30 words
    \item Methods Text :  4124 words.
    \item The Methods section contains 6 tables and 10 figures.
    \item Figure and Table legends in Methods and Supplementary Material are all $<350$ words.  
    \item Figures in the manuscript are shown at their estimated final size.
    \item Total size of the revised main text document is 2.5 MB.
    \item Total size of the Methods+Supplementary+References is 8.5 MB
\end{itemize}


Our point-by-point response to the referees is provided as a separate document.  There are 4 versions: one for each referee with their comments alone, and one that includes all comments together. In addition, we have made adjustments for style, following your guidance.  Where appropriate, these changes are highlighted with purple text in the changetext manuscript.  We have:

\begin{itemize}
\item{re-worded the first paragraph to follow the guidelines you provided.  We believe it now conforms to the Nature Astronomy style, and it is now 200 words according to our count;}
\item{%You encouraged us to archive the data for this manuscript in an accessible, persistent repository. We have 
prepared a github repository (currently private) with all of the code used to construct the key figures in the paper, along with data tables recording the SN photometry.  We will change  this repository to public upon acceptance of the manuscript and include a link in the final published article;}
\item{adjusted figure legends to ensure that they provide a brief description of the figure and the symbols used, within 350 words, including definitions of any error bars employed in the figures;}
\item{adjusted the reference list to keep it at 30 references in the main text;}
\item{added a statement about the corresponding author for data requests, and ensured that we have a statement of author contributions.}
\end{itemize}

Please express our sincere gratitude to the referees for their helpful comments and extraordinary patience.

\bigskip

\noindent Warm Regards,\\
\smallskip
Steve Rodney, on behalf of co-authors


\end{document}