
\begin{thebibliography}{10}
\expandafter\ifx\csname url\endcsname\relax
  \def\url#1{\texttt{#1}}\fi
\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
\providecommand{\bibinfo}[2]{#2}
\providecommand{\eprint}[2][]{\url{#2}}

\bibitem{riess_observational_1998}
\bibinfo{author}{Riess, A.~G.} \emph{et~al.}
\newblock \bibinfo{title}{Observational {Evidence} from {Supernovae} for an
  {Accelerating} {Universe} and a {Cosmological} {Constant}}.
\newblock \emph{\bibinfo{journal}{The Astronomical Journal}}
  \textbf{\bibinfo{volume}{116}}, \bibinfo{pages}{1009--1038}
  (\bibinfo{year}{1998}).
%\newblock \urlprefix\url{http://stacks.iop.org/1538-3881/116/i=3/a=1009}.

\bibitem{perlmutter_measurements_1999}
\bibinfo{author}{Perlmutter, S.} \emph{et~al.}
\newblock \bibinfo{title}{Measurements of $\Omega$ and $\Lambda$ from 42 high-redshift
  supernovae}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{517}}, \bibinfo{pages}{565--586}
  (\bibinfo{year}{1999}).

\bibitem{Riess_large_2019}
\bibinfo{author}{Riess, A.~G.}, \bibinfo{author}{Casertano, S.},
  \bibinfo{author}{Yuan, W.}, \bibinfo{author}{Macri, L.~M.} \&
  \bibinfo{author}{Scolnic, D.}
\newblock \bibinfo{title}{Large {Magellanic} {Cloud} {Cepheid} {Standards}
  {Provide} a 1\% {Foundation} for the {Determination} of the {Hubble}
  {Constant} and {Stronger} {Evidence} for {Physics} beyond Λ{CDM}}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{876}}, \bibinfo{pages}{85} (\bibinfo{year}{2019}).
\newblock
%  \urlprefix\url{https://iopscience.iop.org/article/10.3847/1538-4357/ab1422}.

\bibitem{amendola_cosmology_2013}
\bibinfo{author}{Amendola, L.} \emph{et~al.}
\newblock \bibinfo{title}{Cosmology and fundamental physics with the euclid
  satellite}.
\newblock \emph{\bibinfo{journal}{Living Reviews in Relativity}}
  \textbf{\bibinfo{volume}{16}}, \bibinfo{pages}{6} (\bibinfo{year}{2013}).

\bibitem{spergel_wide_2015}
\bibinfo{author}{Spergel, D.} \emph{et~al.}
\newblock \bibinfo{title}{Wide-field {InfrarRed} survey telescope-astrophysics
  focused telescope assets {WFIRST}-{AFTA} 2015 report}.
\newblock Preprint at \url{https://arxiv.org/abs/1503.03757}
%\emph{\bibinfo{journal}{arXiv e-prints}}
%  \textbf{\bibinfo{volume}{Arxiv:1503.03757}}
(\bibinfo{year}{2015}).

\bibitem{Ivezic_lsst_2019}
\bibinfo{author}{Ivezic} \emph{et~al.}
\newblock \bibinfo{title}{{LSST}: {From} {Science} {Drivers} to {Reference}
  {Design} and {Anticipated} {Data} {Products}}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{873}}, \bibinfo{pages}{111} (\bibinfo{year}{2019}).
\newblock
%  \urlprefix\url{https://iopscience.iop.org/article/10.3847/1538-4357/ab042c}.

\bibitem{aghanim_planck_2018}
\bibinfo{author}{{Planck Collaboration}} \emph{et~al.}
\newblock \bibinfo{title}{Planck 2018 results. {VI}. {Cosmological}
  parameters}.
%\newblock \emph{\bibinfo{journal}{arXiv e-prints}}
%  \textbf{\bibinfo{volume}{arXiv:1807.06209}}
Preprint at \url{https://arxiv.org/abs/1807.06209} 
(\bibinfo{year}{2018}).

\bibitem{verde_tensions_2019}
\bibinfo{author}{Verde, L.}, \bibinfo{author}{Treu, T.} \&
  \bibinfo{author}{Riess, A.~G.}
\newblock \bibinfo{title}{Tensions between the early and late {Universe}}.
\newblock \emph{\bibinfo{journal}{Nature Astronomy}}
  \textbf{\bibinfo{volume}{3}}, \bibinfo{pages}{891--895}
  (\bibinfo{year}{2019}).

\bibitem{einstein_lens_1936}
\bibinfo{author}{Einstein, A.}
\newblock \bibinfo{title}{Lens-like action of a star by the deviation of light
  in the gravitational field}.
\newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{84}},
  \bibinfo{pages}{506--507} (\bibinfo{year}{1936}).

\bibitem{refsdal_possibility_1964}
\bibinfo{author}{Refsdal, S.}
\newblock \bibinfo{title}{On the {Possibility} of {Determining} {Hubble}'s
  {Parameter} and the {Masses} of {Galaxies} from the {Gravitational} {Lens}
  {Effect}}.
\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
  Society}} \textbf{\bibinfo{volume}{128}}, \bibinfo{pages}{307--310}
  (\bibinfo{year}{1964}).
%\newblock
%  \urlprefix\url{https://academic.oup.com/mnras/article/128/4/307/2601707}.

\bibitem{coe_cosmological_2009}
\bibinfo{author}{Coe, D.} \& \bibinfo{author}{Moustakas, L.~A.}
\newblock \bibinfo{title}{Cosmological Constraints from Grvitational Lens Time Delays}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{706}}, \bibinfo{pages}{45--59}
  (\bibinfo{year}{2009}).
\newblock
%  \urlprefix\url{https://iopscience.iop.org/article/10.1088/0004-637X/706/1/45}.

\bibitem{linder_lensing_2011}
\bibinfo{author}{Linder, E.~V.}
\newblock \bibinfo{title}{Lensing time delays and cosmological
  complementarity}.
\newblock \emph{\bibinfo{journal}{Physical Review D}}
  \textbf{\bibinfo{volume}{84}}, \bibinfo{pages}{123529}
  (\bibinfo{year}{2011}).
%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevD.84.123529}.

\bibitem{suyu_cosmology_2014}
\bibinfo{author}{Suyu, S.~H.} \emph{et~al.}
\newblock \bibinfo{title}{Cosmology from Gravitational Lens Time Delays and Planck Data}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{788}}, \bibinfo{pages}{L35} (\bibinfo{year}{2014}).
\newblock
%  \urlprefix\url{https://iopscience.iop.org/article/10.1088/2041-8205/788/2/L35}.

\bibitem{bonvin_cosmograil_2019}
\bibinfo{author}{Bonvin, V.} \emph{et~al.}
\newblock \bibinfo{title}{{COSMOGRAIL}: {XVIII}. Time Delays of the Quadruply  Lensed Wuasar {WFI2033}-4723}.
\newblock \emph{\bibinfo{journal}{Astronomy \& Astrophysics}}
  \textbf{\bibinfo{volume}{629}}, \bibinfo{pages}{A97} (\bibinfo{year}{2019}).
%\newblock \urlprefix\url{https://www.aanda.org/10.1051/0004-6361/201935921}.

\bibitem{wong_h0licow_2019}
\bibinfo{author}{Wong, K.~C.} \emph{et~al.}
\newblock \bibinfo{title}{{H0LiCOW} {XIII}. {A} 2.4\% Measurement of
  \${H}\_\{0\}\$ from Lensed Quasars: \$5.3{\textbackslash}sigma\$ Tension
  Between Early and Late-{Universe} Probes}.
\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
  Society}} \textbf{\bibinfo{volume}{accepted}}, %\bibinfo{pages}{tbd}
\newblock Preprint at \url{http://arxiv.org/abs/1907.04869}
(\bibinfo{year}{2019}).

\bibitem{suyu_cosmological_2018}
\bibinfo{author}{Suyu, S.~H.}, \bibinfo{author}{Chang, T.-C.},
  \bibinfo{author}{Courbin, F.} \& \bibinfo{author}{Okumura, T.}
\newblock \bibinfo{title}{Cosmological {distance} {indicators}}.
\newblock \emph{\bibinfo{journal}{Space Science Reviews}}
  \textbf{\bibinfo{volume}{214}}, \bibinfo{pages}{91} (\bibinfo{year}{2018}).
%\newblock \urlprefix\url{http://link.springer.com/10.1007/s11214-018-0524-3}.

\bibitem{kelly_multiple_2015}
\bibinfo{author}{Kelly, P.~L.} \emph{et~al.}
\newblock \bibinfo{title}{Multiple images of a highly magnified supernova
  formed by an early-type cluster galaxy lens}.
\newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{347}},
  \bibinfo{pages}{1123--1126} (\bibinfo{year}{2015}).
\newblock
%  \urlprefix\url{https://www.sciencemag.org/lookup/doi/10.1126/science.aaa3350}.

\bibitem{goobar_iptf16geu:_2017}
\bibinfo{author}{Goobar, A.} \emph{et~al.}
\newblock \bibinfo{title}{{iPTF16geu}: {A} multiply imaged, gravitationally
  lensed type {Ia} supernova}.
\newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{356}},
  \bibinfo{pages}{291--295} (\bibinfo{year}{2017}).
\newblock
%  \urlprefix\url{http://www.sciencemag.org/lookup/doi/10.1126/science.aal2729}.

\bibitem{kelly_sn_2016}
\bibinfo{author}{Kelly, P.~L.} \emph{et~al.}
\newblock \bibinfo{title}{SN Refsdal: Classification as a luminous and blue SN 1987A-like Type II Supernova}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{831}}, \bibinfo{pages}{205} (\bibinfo{year}{2016}).
\newblock
%  \urlprefix\url{https://iopscience.iop.org/article/10.3847/0004-637X/831/2/205}.

\bibitem{dhawan_magnification_2019}
\bibinfo{author}{Dhawan, S.} \emph{et~al.}
\newblock \bibinfo{title}{Magnification, dust and time-delay constraints from
  the first resolved strongly lensed {Type} {Ia} supernova {iPTF16geu}}.
\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
  Society}} \bibinfo{pages}{stz2965} (\bibinfo{year}{2019}).
\newblock
%  \urlprefix\url{https://academic.oup.com/mnras/advance-article/doi/10.1093/mnras/stz2965/5607803}.

\bibitem{newman_resolving_2018}
\bibinfo{author}{Newman, A.~B.}, \bibinfo{author}{Belli, S.},
  \bibinfo{author}{Ellis, R.~S.} \& \bibinfo{author}{Patel, S.~G.}
\newblock \bibinfo{title}{Resolving {Quiescent} {Galaxies} at \textit{z}$\geq$2.
  {II}. {Direct} {Measures} of {Rotational} {Support}}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{862}}, \bibinfo{pages}{126} (\bibinfo{year}{2018}).
\newblock
%  \urlprefix\url{http://stacks.iop.org/0004-637X/862/i=2/a=126?key=crossref.d984e1694ded7dbef8bab687d5b536be}.

\bibitem{ebeling_macs_2001}
\bibinfo{author}{Ebeling, H.}, \bibinfo{author}{Edge, A.~C.} \&
  \bibinfo{author}{Henry, J.~P.}
\newblock \bibinfo{title}{{MACS}: {A} quest for the most massive galaxy
  clusters in the universe}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{553}}, \bibinfo{pages}{668--676}
  (\bibinfo{year}{2001}).

\bibitem{materials_methods_2020}
\bibinfo{title}{Methods are fully described in the online Methods section}.

\bibitem{jullo_bayesian_2007}
\bibinfo{author}{Jullo, E.} \emph{et~al.}
\newblock \bibinfo{title}{A {Bayesian} approach to strong lensing modelling of
  galaxy clusters}.
\newblock \emph{\bibinfo{journal}{New Journal of Physics}}
  \textbf{\bibinfo{volume}{9}}, \bibinfo{pages}{447--447}
  (\bibinfo{year}{2007}).
\newblock
%  \urlprefix\url{https://iopscience.iop.org/article/10.1088/1367-2630/9/12/447}.

\bibitem{kneib_lenstool_2011}
\bibinfo{author}{Kneib, J.-P.} \emph{et~al.}
\newblock \bibinfo{title}{{LENSTOOL}: {A} gravitational lensing software for
  modeling mass distribution of galaxies and clusters (strong and weak regime)}
  \bibinfo{pages}{ascl:1102.004} (\bibinfo{year}{2011}).

\bibitem{woosley_type_2007}
\bibinfo{author}{Woosley, S.~E.}, \bibinfo{author}{Kasen, D.},
  \bibinfo{author}{Blinnikov, S.} \& \bibinfo{author}{Sorokina, E.}
\newblock \bibinfo{title}{Type {Ia} {Supernova} {Light} {Curves}}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{662}}, \bibinfo{pages}{487--503}
  (\bibinfo{year}{2007}).
%\newblock \urlprefix\url{http://stacks.iop.org/0004-637X/662/i=1/a=487}.

\bibitem{kasen_type_2009}
\bibinfo{author}{Kasen, D.} \& \bibinfo{author}{Woosley, S.~E.}
\newblock \bibinfo{title}{Type II Supernovae: Model light curves and standard candle relationships}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{703}}, \bibinfo{pages}{2205--2216}
  (\bibinfo{year}{2009}).
\newblock
%  \urlprefix\url{http://stacks.iop.org/0004-637X/703/i=2/a=2205?key=crossref.208d40b300652b1e492e00d8bcc4f81f}.

\bibitem{oguri_gravitationally_2010}
\bibinfo{author}{Oguri, M.} \& \bibinfo{author}{Marshall, P.~J.}
\newblock \bibinfo{title}{Gravitationally lensed quasars and supernovae in
  future wide-field optical imaging surveys: {Lensed} quasars and supernovae}.
\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
  Society}} \textbf{\bibinfo{volume}{405}}, \bibinfo{pages}{2579--2593}
  (\bibinfo{year}{2010}).
\newblock
%  \urlprefix\url{https://academic.oup.com/mnras/article-lookup/doi/10.1111/j.1365-2966.2010.16639.x}.

\bibitem{goldstein_rates_2019}
\bibinfo{author}{Goldstein, D.~A.}, \bibinfo{author}{Nugent, P.~E.} \&
  \bibinfo{author}{Goobar, A.}
\newblock \bibinfo{title}{Rates and {Properties} of {Supernovae} {Strongly}
  {Gravitationally} {Lensed} by {Elliptical} {Galaxies} in {Time}-domain
  {Imaging} {Surveys}}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal Supplement Series}}
  \textbf{\bibinfo{volume}{243}}, \bibinfo{pages}{6} (\bibinfo{year}{2019}).
\newblock
%  \urlprefix\url{https://iopscience.iop.org/article/10.3847/1538-4365/ab1fe0}.

\bibitem{wojtak_magnified_2019}
\bibinfo{author}{Wojtak, R.}, \bibinfo{author}{Hjorth, J.} \&
  \bibinfo{author}{Gall, C.}
\newblock \bibinfo{title}{Magnified or multiply imaged? - {Search} strategies
  for gravitationally lensed supernovae in wide-field surveys}.
\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
  Society}} \textbf{\bibinfo{volume}{487}}, \bibinfo{pages}{3342--3355}
  (\bibinfo{year}{2019}).

\bibitem{gonzaga_drizzlepac_2012}
\bibinfo{author}{Gonzaga, S.} \& \bibinfo{author}{{et al.}}
\newblock \emph{\bibinfo{title}{The {DrizzlePac} handbook}}
  (\bibinfo{year}{2012}).

\bibitem{the_astropy_collaboration_astropy_2018}
\bibinfo{author}{{The Astropy Collaboration}} \emph{et~al.}
\newblock \bibinfo{title}{The {Astropy} {Project}: {Building} an {Open}-science
  {Project} and {Status} of the v2.0 {Core} {Package}}.
\newblock \emph{\bibinfo{journal}{The Astronomical Journal}}
  \textbf{\bibinfo{volume}{156}}, \bibinfo{pages}{123} (\bibinfo{year}{2018}).
\newblock
%  \urlprefix\url{https://iopscience.iop.org/article/10.3847/1538-3881/aabc4f}.

\bibitem{weilbacher_data_2020}
\bibinfo{author}{Weilbacher, P.~M.} \emph{et~al.}
\newblock \bibinfo{title}{The data processing pipeline for the {MUSE}
  instrument}.
%\newblock \emph{\bibinfo{journal}{arXiv e-prints}}
%\textbf{\bibinfo{volume}{arXiv:2006.08638}}
Preprint at \url{https://arxiv.org/abs/2006.08638}
(\bibinfo{year}{2020}).

\bibitem{bacon_muse_2017}
\bibinfo{author}{Bacon, R.} \emph{et~al.}
\newblock \bibinfo{title}{The {MUSE} \textit{{Hubble}} {Ultra} {Deep} {Field}
  {Survey}: {I}. {Survey} description, data reduction, and source detection}.
\newblock \emph{\bibinfo{journal}{Astronomy \& Astrophysics}}
  \textbf{\bibinfo{volume}{608}}, \bibinfo{pages}{A1} (\bibinfo{year}{2017}).
%\newblock \urlprefix\url{http://www.aanda.org/10.1051/0004-6361/201730833}.

\bibitem{soto_zap_2016}
\bibinfo{author}{Soto, K.~T.}, \bibinfo{author}{Lilly, S.~J.},
  \bibinfo{author}{Bacon, R.}, \bibinfo{author}{Richard, J.} \&
  \bibinfo{author}{Conseil, S.}
\newblock \bibinfo{title}{{ZAP} - enhanced {PCA} sky subtraction for integral
  field spectroscopy}.
\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
  Society}} \textbf{\bibinfo{volume}{458}}, \bibinfo{pages}{3210--3220}
  (\bibinfo{year}{2016}).

\bibitem{piqueras_mpdaf_2019}
\bibinfo{author}{Piqueras, L.} \emph{et~al.}
\newblock \bibinfo{title}{{MPDAF} - a python package for the analysis of
  {VLT}/{MUSE} data}.
\newblock In \bibinfo{editor}{Molinaro, M.}, \bibinfo{editor}{Shortridge, K.}
  \& \bibinfo{editor}{Pasian, F.} (eds.) \emph{\bibinfo{booktitle}{Astronomical
  data analysis software and systems {XXVI}}}, vol. \bibinfo{volume}{521} of
  \emph{\bibinfo{series}{Astronomical society of the pacific conference
  series}}, \bibinfo{pages}{545} (\bibinfo{year}{2019}).

\bibitem{mahler_strong_2018}
\bibinfo{author}{Mahler, G.} \emph{et~al.}
\newblock \bibinfo{title}{Strong-lensing analysis of {A2744} with {MUSE} and
  hubble frontier fields images}.
\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
  Society}} \textbf{\bibinfo{volume}{473}}, \bibinfo{pages}{663--692}
  (\bibinfo{year}{2018}).

\bibitem{lagattuta_probing_2019}
\bibinfo{author}{Lagattuta, D.~J.} \emph{et~al.}
\newblock \bibinfo{title}{Probing {3D} structure with a large {MUSE} mosaic:
  extending the mass model of {Frontier} {Field} {Abell} 370}.
\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
  Society}} \textbf{\bibinfo{volume}{485}}, \bibinfo{pages}{3738--3760}
  (\bibinfo{year}{2019}).

\bibitem{richard_mass_2014}
\bibinfo{author}{Richard, J.} \emph{et~al.}
\newblock \bibinfo{title}{Mass and magnification maps for the {Hubble} {Space}
  {Telescope} {Frontier} {Fields} clusters: implications for high-redshift
  studies}.
\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
  Society}} \textbf{\bibinfo{volume}{444}}, \bibinfo{pages}{268--289}
  (\bibinfo{year}{2014}).

\bibitem{richard_locuss_2010}
\bibinfo{author}{Richard, J.} \emph{et~al.}
\newblock \bibinfo{title}{{LoCuSS}: first results from strong-lensing analysis
  of 20 massive galaxy clusters at z = 0.2}.
\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
  Society}} \textbf{\bibinfo{volume}{404}}, \bibinfo{pages}{325--349}
  (\bibinfo{year}{2010}).

\bibitem{mannucci_supernova_2005}
\bibinfo{author}{Mannucci, F.} \emph{et~al.}
\newblock \bibinfo{title}{The supernova rate per unit mass}.
\newblock \emph{\bibinfo{journal}{Astronomy \& Astrophysics}}
  \textbf{\bibinfo{volume}{433}}, \bibinfo{pages}{807--814}
  (\bibinfo{year}{2005}).
%\newblock \urlprefix\url{http://www.aanda.org/10.1051/0004-6361:20041411}.

\bibitem{newman_resolving_2018-1}
\bibinfo{author}{Newman, A.~B.}, \bibinfo{author}{Belli, S.},
  \bibinfo{author}{Ellis, R.~S.} \& \bibinfo{author}{Patel, S.~G.}
\newblock \bibinfo{title}{Resolving {Quiescent} {Galaxies} at \textit{z}$\geq$2.
  {I}. {Search} for {Gravitationally} {Lensed} {Sources} and {Characterization}
  of {Their} {Structure}, {Stellar} {Populations}, and {Line} {Emission}}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{862}}, \bibinfo{pages}{125} (\bibinfo{year}{2018}).
\newblock
%  \urlprefix\url{http://stacks.iop.org/0004-637X/862/i=2/a=125?key=crossref.11a8992d65c44e536887566650da59f8}.

\bibitem{foley_classifying_2013}
\bibinfo{author}{Foley, R.~J.} \& \bibinfo{author}{Mandel, K.}
\newblock \bibinfo{title}{Classifying supernovae using only galaxy data}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{778}}, \bibinfo{pages}{167} (\bibinfo{year}{2013}).
\newblock
%  \urlprefix\url{http://stacks.iop.org/0004-637X/778/i=2/a=167?key=crossref.ed447fe9ba93137547a570f6beb359f8}.

\bibitem{smartt_progenitors_2009}
\bibinfo{author}{Smartt, S.~J.}
\newblock \bibinfo{title}{Progenitors of {Core}-{Collapse} {Supernovae}}.
\newblock \emph{\bibinfo{journal}{Annual Review of Astronomy and Astrophysics}}
  \textbf{\bibinfo{volume}{47}}, \bibinfo{pages}{63--106}
  (\bibinfo{year}{2009}).
%\newblock \urlprefix\url{https://doi.org/10.1146/annurev-astro-082708-101737}.

\bibitem{li_rates_2012}
\bibinfo{author}{Li, X.}, \bibinfo{author}{Hjorth, J.} \&
  \bibinfo{author}{Richard, J.}
\newblock \bibinfo{title}{The rates and time-delay distribution of multiply
  imaged supernovae behind lensing clusters}.
\newblock \emph{\bibinfo{journal}{Journal of Cosmology and Astroparticle
  Physics}} \textbf{\bibinfo{volume}{2012}}, \bibinfo{pages}{015--015}
  (\bibinfo{year}{2012}).
\newblock
%  \urlprefix\url{https://iopscience.iop.org/article/10.1088/1475-7516/2012/11/015}.

\bibitem{barbary_sncosmo_2016}
\bibinfo{author}{Barbary, K.} \emph{et~al.}
\newblock \bibinfo{title}{Sncosmo/{Sncosmo}: {V1}.4.0} (\bibinfo{year}{2016}).
\newblock \urlprefix\url{10.5281/zenodo.168220}.

\bibitem{rodney_type_2014}
\bibinfo{author}{Rodney, S.~A.} \emph{et~al.}
\newblock \bibinfo{title}{{Type} {Ia} {Supernova} {Rate} {Measurements} {to}
  {Redshift} 2.5 {From} {CANDELS}: {Searching} {for} {{}rompt} {Explosions} {in}
  the {Early} {Universe}}.
\newblock \emph{\bibinfo{journal}{The Astronomical Journal}}
  \textbf{\bibinfo{volume}{148}}, \bibinfo{pages}{13} (\bibinfo{year}{2014}).
\newblock
%  \urlprefix\url{http://stacks.iop.org/1538-3881/148/i=1/a=13?key=crossref.807cb4ea3e88cb99df642470efc9173f}.

\bibitem{guy_salt2:_2007}
\bibinfo{author}{Guy, J.} \emph{et~al.}
\newblock \bibinfo{title}{{SALT2}: using distant supernovae to improve the use
  of type {Ia} supernovae as distance indicators}.
\newblock \emph{\bibinfo{journal}{Astronomy \& Astrophysics}}
  \textbf{\bibinfo{volume}{466}}, \bibinfo{pages}{11--21}
  (\bibinfo{year}{2007}).
%\newblock \urlprefix\url{http://www.aanda.org/10.1051/0004-6361:20066930}.

\bibitem{pierel_extending_2018}
\bibinfo{author}{Pierel, J. D.~R.} \emph{et~al.}
\newblock \bibinfo{title}{Extending {Supernova} {Spectral} {Templates} for
  {Next}-generation {Space} {Telescope} {Observations}}.
\newblock \emph{\bibinfo{journal}{Publications of the Astronomical Society of
  the Pacific}} \textbf{\bibinfo{volume}{130}}, \bibinfo{pages}{114504}
  (\bibinfo{year}{2018}).
\newblock
%  \urlprefix\url{http://stacks.iop.org/1538-3873/130/i=993/a=114504?key=crossref.44ee315a73acf8a52666778cf6cc1881}.

\bibitem{kessler_snana:_2009}
\bibinfo{author}{Kessler, R.} \emph{et~al.}
\newblock \bibinfo{title}{{SNANA}: {A} {Public} {Software} {Package} for
  {Supernova} {Analysis}}.
\newblock \emph{\bibinfo{journal}{Publications of the Astronomical Society of
  the Pacific}} \textbf{\bibinfo{volume}{121}}, \bibinfo{pages}{1028--1035}
  (\bibinfo{year}{2009}).
%\newblock \urlprefix\url{http://iopscience.iop.org/article/10.1086/605984}.

\bibitem{frieman_sloan_2008}
\bibinfo{author}{Frieman, J.~A.} \emph{et~al.}
\newblock \bibinfo{title}{The Sloan Digital Sky Survey-II Supernova Survey: Technical Summary}.
\newblock \emph{\bibinfo{journal}{The Astronomical Journal}}
  \textbf{\bibinfo{volume}{135}}, \bibinfo{pages}{338--347}
  (\bibinfo{year}{2008}).
\newblock
%  \urlprefix\url{https://iopscience.iop.org/article/10.1088/0004-6256/135/1/338}.

\bibitem{sako_sloan_2008}
\bibinfo{author}{Sako, M.} \emph{et~al.}
\newblock \bibinfo{title}{The Sloan Digital Sky Survey-II Supernova Survey: Search Algorithm and Follow-up Observations}.
\newblock \emph{\bibinfo{journal}{The Astronomical Journal}}
  \textbf{\bibinfo{volume}{135}}, \bibinfo{pages}{348--373}
  (\bibinfo{year}{2008}).
\newblock
%  \urlprefix\url{https://iopscience.iop.org/article/10.1088/0004-6256/135/1/348}.

\bibitem{dandrea_type_2010}
\bibinfo{author}{D'Andrea, C.~B.} \emph{et~al.}
\newblock \bibinfo{title}{Type II-P Supernovae from the SDSS-II Supernova Survey and the standardized candle method}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{708}}, \bibinfo{pages}{661--674}
  (\bibinfo{year}{2010}).
\newblock
%  \urlprefix\url{https://iopscience.iop.org/article/10.1088/0004-637X/708/1/661}.

\bibitem{astier_supernova_2006}
\bibinfo{author}{Astier, P.} \emph{et~al.}
\newblock \bibinfo{title}{The {Supernova} {Legacy} {Survey}: measurement of
  $\Omega_{\mathsf{M}}$,   $\Omega_{\mathsf{\Lambda}}$,
  and $w$ from the first year data set}.
\newblock \emph{\bibinfo{journal}{Astronomy \& Astrophysics}}
  \textbf{\bibinfo{volume}{447}}, \bibinfo{pages}{31--48}
  (\bibinfo{year}{2006}).
%\newblock \urlprefix\url{http://www.aanda.org/10.1051/0004-6361:20054185}.

\bibitem{hamuy_carnegie_2006}
\bibinfo{author}{Hamuy, M.} \emph{et~al.}
\newblock \bibinfo{title}{The {Carnegie} {Supernova} {Project}: {The}
  {Low}-{Redshift} {Survey}}.
\newblock \emph{\bibinfo{journal}{Publications of the Astronomical Society of
  the Pacific}} \textbf{\bibinfo{volume}{118}}, \bibinfo{pages}{2--20}
  (\bibinfo{year}{2006}).
%\newblock \urlprefix\url{http://iopscience.iop.org/article/10.1086/500228}.

\bibitem{stritzinger_he-rich_2009}
\bibinfo{author}{Stritzinger, M.} \emph{et~al.}
\newblock \bibinfo{title}{The He-Rich Core-collapse Supernova 2007Y: Observations from X-ray to radio wavelengths}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{696}}, \bibinfo{pages}{713--728}
  (\bibinfo{year}{2009}).
\newblock
%  \urlprefix\url{https://iopscience.iop.org/article/10.1088/0004-637X/696/1/713}.

\bibitem{morrell_carnegie_2012}
\bibinfo{author}{Morrell, N.~I.}
\newblock \bibinfo{title}{Carnegie supernova project: {Spectroscopic}
  observations of core collapse supernovae}.
\newblock In \bibinfo{editor}{Roming, P.}, \bibinfo{editor}{Kawai, N.} \&
  \bibinfo{editor}{Pian, E.} (eds.) \emph{\bibinfo{booktitle}{Death of massive
  stars: {Supernovae} and gamma-ray bursts}}, vol. \bibinfo{volume}{279} of
  \emph{\bibinfo{series}{{IAU} symposium}}, \bibinfo{pages}{361--362}
  (\bibinfo{year}{2012}).

\bibitem{pierel_turning_2019}
\bibinfo{author}{Pierel, J. D.~R.} \& \bibinfo{author}{Rodney, S.}
\newblock \bibinfo{title}{Turning {Gravitationally} {Lensed} {Supernovae} into
  {Cosmological} {Probes}}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{876}}, \bibinfo{pages}{107} (\bibinfo{year}{2019}).
\newblock
%  \urlprefix\url{https://iopscience.iop.org/article/10.3847/1538-4357/ab164a}.

\bibitem{huber_strongly_2019}
\bibinfo{author}{Huber, S.} \emph{et~al.}
\newblock \bibinfo{title}{Strongly lensed {SNe} {Ia} in the era of {LSST}:
  observing cadence for lens discoveries and time-delay measurements}.
\newblock \emph{\bibinfo{journal}{Astronomy \& Astrophysics}}
  \textbf{\bibinfo{volume}{631}}, \bibinfo{pages}{A161} (\bibinfo{year}{2019}).
%\newblock \urlprefix\url{https://www.aanda.org/10.1051/0004-6361/201935370}.

\bibitem{goldstein_precise_2018}
\bibinfo{author}{Goldstein, D.~A.}, \bibinfo{author}{Nugent, P.~E.},
  \bibinfo{author}{Kasen, D.~N.} \& \bibinfo{author}{Collett, T.~E.}
\newblock \bibinfo{title}{Precise {Time} {Delays} from {Strongly}
  {Gravitationally} {Lensed} {Type} {Ia} {Supernovae} with {Chromatically}
  {Microlensed} {Images}}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{855}}, \bibinfo{pages}{22} (\bibinfo{year}{2018}).
\newblock
%  \urlprefix\url{http://stacks.iop.org/0004-637X/855/i=1/a=22?key=crossref.0c66b370adee53fbbf39e00b6f7f9f0d}.

\bibitem{foxley-marrable_impact_2018}
\bibinfo{author}{Foxley-Marrable, M.}, \bibinfo{author}{Collett, T.~E.},
  \bibinfo{author}{Vernardos, G.}, \bibinfo{author}{Goldstein, D.~A.} \&
  \bibinfo{author}{Bacon, D.}
\newblock \bibinfo{title}{The impact of microlensing on the standardization of
  strongly lensed {Type} {Ia} supernovae}.
\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
  Society}} \textbf{\bibinfo{volume}{478}}, \bibinfo{pages}{5081--5090}
  (\bibinfo{year}{2018}).
\newblock
%  \urlprefix\url{https://academic.oup.com/mnras/article/478/4/5081/5001437}.

\bibitem{bonvin_impact_2019}
\bibinfo{author}{Bonvin, V.} \emph{et~al.}
\newblock \bibinfo{title}{Impact of the {3D} source geometry on time-delay
  measurements of lensed type-{Ia} supernovae}.
\newblock \emph{\bibinfo{journal}{Astronomy \& Astrophysics}}
  \textbf{\bibinfo{volume}{621}}, \bibinfo{pages}{A55} (\bibinfo{year}{2019}).
%\newblock \urlprefix\url{https://www.aanda.org/10.1051/0004-6361/201833405}.

\bibitem{kochanek_quantitative_2004}
\bibinfo{author}{Kochanek, C.~S.}
\newblock \bibinfo{title}{Quantitative {Interpretation} of {Quasar}
  {Microlensing} {Light} {Curves}}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{605}}, \bibinfo{pages}{58--77}
  (\bibinfo{year}{2004}).
%\newblock \urlprefix\url{https://iopscience.iop.org/article/10.1086/382180}.

\bibitem{vernardos_joint_2018}
\bibinfo{author}{Vernardos, G.}
\newblock \bibinfo{title}{A joint microlensing analysis of lensing mass and
  accretion disc models}.
\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
  Society}} \textbf{\bibinfo{volume}{480}}, \bibinfo{pages}{4675--4683}
  (\bibinfo{year}{2018}).
\newblock
%  \urlprefix\url{https://academic.oup.com/mnras/article/480/4/4675/5067321}.

\bibitem{hsiao_k_2007}
\bibinfo{author}{Hsiao, E.~Y.} \emph{et~al.}
\newblock \bibinfo{title}{\textit{{K}}-{Corrections} and {Spectral} {Templates} of {Type} {Ia} {Supernovae}}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{663}}, \bibinfo{pages}{1187--1200}
  (\bibinfo{year}{2007}).
%\newblock \urlprefix\url{http://stacks.iop.org/0004-637X/663/i=2/a=1187}.

\bibitem{kessler_results_2010}
\bibinfo{author}{Kessler, R.} \emph{et~al.}
\newblock \bibinfo{title}{Results from the {Supernova} {Photometric}
  {Classification} {Challenge}}.
\newblock \emph{\bibinfo{journal}{Publications of the Astronomical Society of
  the Pacific}} \textbf{\bibinfo{volume}{122}}, \bibinfo{pages}{1415--1431}
  (\bibinfo{year}{2010}).
%\newblock \urlprefix\url{http://iopscience.iop.org/article/10.1086/657607}.

\bibitem{wang_determination_2006}
\bibinfo{author}{Wang, X.}, \bibinfo{author}{Wang, L.}, \bibinfo{author}{Pain,
  R.}, \bibinfo{author}{Zhou, X.} \& \bibinfo{author}{Li, Z.}
\newblock \bibinfo{title}{Determination of the {Hubble} {Constant}, the
  {Intrinsic} {Scatter} of {Luminosities} of {Type} {Ia} {Supernovae}, and
  {Evidence} for {Nonstandard} {Dust} in {Other} {Galaxies}}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{645}}, \bibinfo{pages}{488--505}
  (\bibinfo{year}{2006}).
%\newblock \urlprefix\url{https://iopscience.iop.org/article/10.1086/504312}.

\bibitem{mosher_cosmological_2014}
\bibinfo{author}{Mosher, J.} \emph{et~al.}
\newblock \bibinfo{title}{Cosmological parameter uncertainties from SALT-II Type Ia supernova light curve models}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{793}}, \bibinfo{pages}{16} (\bibinfo{year}{2014}).
\newblock
%  \urlprefix\url{http://stacks.iop.org/0004-637X/793/i=1/a=16?key=crossref.a750658756be980048b20e0e45ff2129}.

\end{thebibliography}

